\Large{All in the family:\\Anna and Lisa Hahner's finishing times in\\the 2016 women's Olympic marathon}

### 2017-02-03 paper/paper.tex
paper stuff

\begin{figure}[!ht]
  \centering
  \caption{Distribution of simulated results for the Hahner twins (using halfway split as predictor)}
  \label{fig:simdiffhalf} 
  \begin{subfigure}{.45\textwidth}
    \includegraphics[width=\textwidth,
    keepaspectratio]{simulated_time_half.pdf}
    \caption{Simulated differences in finishing times}
    \label{fig:simulatedfinishtimes}
  \end{subfigure}
  \begin{subfigure}{.45\textwidth}
    \includegraphics[width=\textwidth, keepaspectratio]{simulated_rank_half.pdf}
    \caption{Simulated differences in places}
    \label{fig:simulatedranks}
  \end{subfigure}
\end{figure}

@@

\newpage
\section*{Further reading}

>>>>

\begin{figure}[!ht]
  \centering
  \caption{Distribution of simulated results for the Hahner twins
    based on half marathon split}
  \label{fig:simdiffhalf} 
  \begin{subfigure}{.45\textwidth}
    \includegraphics[width=\textwidth,
    keepaspectratio]{simulated_time_half.pdf}
    \caption{Simulated differences in finishing times}
    \label{fig:simulatedfinishtimes}
  \end{subfigure}
  \begin{subfigure}{.45\textwidth}
    \includegraphics[width=\textwidth, keepaspectratio]{simulated_rank_half.pdf}
    \caption{Simulated differences in places}
    \label{fig:simulatedranks}
  \end{subfigure}
\end{figure}

An important point regarding our simulations is the way that we
handled DNFs.  As our description above indicates, we assumed that DNF
probabilities are the same for all runners and that the likelihood of
a DNF is a not function of a runner's anticipated marathon finishing
time.  The rug marks in Figure \ref{fig:45degreeplot} suggest that
runners with better personal best times may be more likely to DNF than
other runners, \emph{ceteris paribus}.  We suspect that this occurs
because some better runners may expend excessive energy trying to
achieve a good result in the marathon and in so doing injure or
exhaust themselves; lesser runners, in contrast, may be content to
finish respectably.  Regardless of the validity of this conjecture,
Figure \ref{fig:45degreeplot} shows that the Hahner twins are
representative of sort of runners who DNFed in Rio.  Since our
simulated Hahner statistics are conditioned on both Hahner twins
finishing, it follows that they are conservative.  The fact that both
women finished the marathon was notable in and of itself, and by
discounting the possibility of a Hahner DNF we are giving the benefit
of the doubt to the Hahner twins.

Turning back to the motivation of this article, we have offered two
perspectives on Anna and Lisa Hahner'

@@

\section*{Further reading}
